---
title: "Pitchfork scraper"
author: "Szabolcs Kerekes"
date: "19/04/2019"
output: html_document
---

The following document details the process of getting the review informations from pitchfork.com.

## Setup
We start with setting up the environment via loading the required packages.

```{r setup, results="hide", message=F, warning = F}
library(rvest)
library(data.table)
library(jsonlite)
library(httr)
library(lubridate)
library(dplyr)
library(tidyverse)
```

## Defining functions
Next we define the functions we use for scraping the website. The working of each functions is detailed in the comments.

```{r functions}
# This function gets the review link for each individual review.
get_link_review <- function(url){
  
  my_page <- read_html(url)
  
  review_link<- 
    my_page%>%
    html_nodes('.review__link')%>%
    html_attr('href')

    return(review_link)
}

# This function gets the 'Best New Music' tags.
get_bnm <- function(url){
  
  my_page <- read_html(url)
  
  artist<-
    my_page%>%
    html_nodes('.review__title-artist')%>%
    html_text()
  
  album_name<-
    my_page%>%
    html_nodes('.review__title-album')%>%
    html_text()
  
  date<-
    my_page%>%
    html_nodes('.pub-date')%>%
    html_text()
  
  t <- data.frame('artist'= artist, 'album_name' = album_name, 'date' = date, stringsAsFactors = F)
  return(t)
}

# This function gets the review details.
get_review_data <- function(url){
  
  my_page <- read_html(url)
  
  artist<-
    my_page%>%
    html_node('.single-album-tombstone__artist-links')%>%
    html_text()  
  
  album_name<-
    my_page%>%
    html_node('.single-album-tombstone__review-title')%>%
    html_text()  
  
  date<-
    my_page%>%
    html_node('.pub-date')%>%
    html_text() 
  
  p_score<-
    my_page%>%
    html_node('.score')%>%
    html_text()
  
  genre<-
    my_page%>%
    html_node('.genre-list__link')%>%
    html_text()
  
  release_year<-
    my_page%>%
    html_node('.single-album-tombstone__meta-year')%>%
    html_text()   
  
  author_name<-
    my_page%>%
    html_node('.authors-detail__display-name')%>%
    html_text()
  
  author_title<-
    my_page%>%
    html_node('.authors-detail__title')%>%
    html_text()
  
  label_name<-
    my_page%>%
    html_node('.labels-list__item')%>%
    html_text
  
  review_text<-
    my_page%>%
    html_nodes('p')%>%
    html_text
  
  t <- data.frame('artist' = artist, 'album_name' = album_name, 'date' = date,  'p_score'= p_score, 'genre' = genre, 'release_year' = release_year, 'author_name' = author_name, 'author_title' = author_title, 'label_name' = label_name,
 'review_text' = review_text, stringsAsFactors = F)
  
  return(t)
}
```

## Getting the individual lage links
The following code chunk details the process of getting the individual links to the reviews. It also includes the creation of the links to the 'Best New Music' articles.

```{r getting pages}
# Here can be set the number of articles to be scraped, each page contains 12 articles
page_count <- 2
album_count <- page_count * 12
page_number <- c(seq(1,page_count,1))

# We create the links to the pages
page_link <- rep("https://pitchfork.com/reviews/albums/?page=", length(page_number))
all_page_links <- paste0(page_link, page_number)

# We get the individual review links
pitchfork_final_table <- NULL

for(i in 1:page_count){
  pitchfork_data_links <- get_link_review(all_page_links[i])
  pitchfork_final_table <- c(pitchfork_final_table, pitchfork_data_links)
}

# We get rid of any duplicates
full_link_list <- unique(pitchfork_final_table)

# We create the exact links to be used later
link_begin <- rep("https://pitchfork.com", length(full_link_list))
indiv_links <- paste0(link_begin, full_link_list)

# We do the same for the reviews tagged as 'Best New Music' 
page_count_bnm <- 1
page_number_bnm <- c(seq(1,page_count_bnm,1))
page_link_bnm <- rep("https://pitchfork.com/reviews/best/albums/?page=", length(page_number_bnm))
all_page_links_bnm <- paste0(page_link_bnm, page_number_bnm)
```

## Downloading the review details.
As a next step we scrap the individual review pages and the 'Best New Music' information for each review.

```{r getting scores}
# The time measurement is only used for estimating the expected runtime 
use_time <- FALSE
if (use_time == TRUE){
  start_time <- Sys.time()
}

pitchfork_data_aggreg_bnm <- NULL

# We run the following loop with a sleep element to avoid IP blockage
for(i in 1:page_count_bnm){
  pitchfork_data_aggreg_prep_bnm <- get_bnm(all_page_links_bnm[i])
  pitchfork_data_aggreg_bnm <- rbind(pitchfork_data_aggreg_bnm, pitchfork_data_aggreg_prep_bnm)
  if (i %% 5 == 0){
    Sys.sleep(1)
  }
}

pitchfork_score_post <- NULL
pitchfork_score_prep <- NULL

# We run the following loop with a sleep element to avoid IP blockage
for(i in 1:album_count){
  pitchfork_score_prep <- tryCatch(get_review_data(indiv_links[i]), error = function(e) c(0,0,0,0,0,0))
  pitchfork_score_post <- rbind(pitchfork_score_post, pitchfork_score_prep)
    if (i %% 5 == 0){
    Sys.sleep(1)
    }
}

if (use_time == TRUE){
  end_time <- Sys.time()
run_time_scores <- end_time - start_time
paste0("Scoring loop run for: ", run_time_scores)
}
```

We need to merge all of the reviews into one entry as now they are still in separate line per entries.

```{r aggregator}
# We create IDs for the selections
pitchfork_score_post <- pitchfork_score_post %>% mutate(id = paste0(paste0(artist, album_name),date))
unique_albums <- unique(pitchfork_score_post$id)

temp_df <- data.frame()

# We merge the review text data into one and add it back to the original file
for (i in unique_albums){
  reviews <- pitchfork_score_post %>% select(id, review_text) %>% filter(id == i)
  review_total <- c()
  for (r in reviews$review_text){
    review_total <- paste(review_total, r)
  }
  reviews <- pitchfork_score_post %>% filter(id == i)
  reviews <- head(reviews, 1)
  reviews$review_text <- review_total
  temp_df <- rbind(temp_df, reviews)
}

pitchfork_score_post <- temp_df %>% select(-id)
```

## Initial data cleaning
Here we do some cleaning of the data, including merging the original and 'Best New Music' data, as well as adjusting variable types and column names.

```{r data adjusted, warning=FALSE}
# We add the links to the review data
results_matrix <- NULL
results_matrix <- cbind(pitchfork_score_post, indiv_links)
colnames(results_matrix) <- c("artist", "album", "date", "score", "genre", "release_year", "author_name", "author_title", "label_name", "review_text", "link")
results_matrix_dt <- data.table(results_matrix)

# We create dummies for the 'Best New Music' albums
bnm_stats <- data.table(pitchfork_data_aggreg_bnm)
bnm_stats[, bnm := TRUE,]
bnm_stats[, id := paste0(artist, album_name, date), ]

# We merge the two datasets
results_matrix_dt[, id := paste0(artist, album, date), ]
results_matrix_bnm <- left_join(results_matrix_dt, bnm_stats, by = 'id')

# We adjust and rename the variables in the merged data
results_matrix_bnm <- data.table(results_matrix_bnm)
results_matrix_bnm[, c("artist.y", "album_name", "date.y") := NULL, ]
colnames(results_matrix_bnm) <- c("artist", "album", "review_date", "score", "genre", "release_year", "author_name", "author_title", "label_name", "review_text", "link", "id", "bnm")

# We do some further adjustments to the variables
results_matrix_bnm[, review_date := mdy(review_date), ]
results_matrix_bnm$score <- as.numeric(results_matrix_bnm$score)
results_matrix_bnm$genre <- as.factor(results_matrix_bnm$genre)
results_matrix_bnm$release_year <- as.numeric(sub("• ","", results_matrix_bnm$release_year))

```

## Saving the data
Finally we save the data into a csv type file.

```{r saving}
write.csv(results_matrix_bnm, 'data/pitchfork_final.csv',row.names = FALSE)
```
